\section[Bayesian Estimation of Quarterly Inflation]{Bayesian Estimation of Quarterly Inflation\label{ex:BayesianEstimationQuarterlyInflation}}
Perform a Bayesian estimation using the Gibbs sampler of an autoregressive model with two lags of quarterly US inflation
\begin{align*}
y_t = c + \phi_1 y_{t-1} + \phi_2 y_{t-2} + u_t = Y_{t-1} \theta + u_t
\end{align*}
where \(Y_{t-1}=(1,y_{t-1},y_{t-2})\), \(u_t\sim WN(0,\sigma_u^2)\) and \(\theta = (c,\phi_1,\phi_2)'\).
To this end, assume a Gamma distribution for the marginal prior for the precision \(\frac{1}{\sigma_u^2}\)
  and a normal distribution for the conditional prior for the coefficients \(\theta \) given \(\frac{1}{\sigma_u^2}\).

\begin{enumerate}

\item Load the dataset \texttt{QuarterlyInflation.csv}.
It contains a series for US quarterly inflation from 1947Q1 to 2012Q3.
Plot the data.

\item Create the matrix of regressors and the corresponding vector of endogenous variables for an AR{(2)} model with a constant.

\item Set the prior mean for the coefficients to a vector of zeros, \(\theta_0 = 0\),
  and the prior covariance matrix to the identity matrix, \(\Sigma_{0}=I\).

\item Set the shape parameter for the variance parameter to \(s_0=1\)
  and the scale parameter to \(v_0=0.1\).

\item Set the total number of Gibbs iterations to \(R=50000\) with a burn-in phase of \(B=40000\).

\item Initialize output matrices for the remaining \(R-B\) draws of the coefficient estimates and the variance estimate.

\item Initialize the first draw of \(\frac{1}{\sigma_u^2}\) to its OLS estimate.

\item For \(j=1,\ldots ,R\) do the following

\begin{enumerate}

  \item Sample \(\theta(j)\) conditional on \(\frac{1}{\sigma_u^2(j)}\) from \(\mathcal{N}(\theta_1,\Sigma_{1})\) where
  \begin{align*}
  \Sigma_{1} &= {(\Sigma_{0}^{-1} +\sigma_u^{-2}(j)(X'X))}^{-1}
  \\
  \theta_1 &= \Sigma_{1} \cdot (\Sigma_{0}^{-1}\phi_0 + \sigma_u^{-2}(j) X'y)
  \end{align*}
  Optionally: check the stability of the draw to avoid an explosive AR processes.

  \item Sample \(1/\sigma_u^2(j)\) conditional on \(\theta(j)\) from the Gamma distribution \(G(s_1,v_1)\)
  where
  \begin{align*}
  s_1 &= s_0 + T
  \\
  v_1 &= v_0 + \sum_{t=3}^T {(y_t-Y_{t-1}\theta(j))}^2
  \end{align*}

  \item If you passed the burn-in phase (\(j>B\)),
    then save the draws of \(\theta(j)\) and \(\sigma^2(j)\) into the output matrices.

\end{enumerate}

\item Plot the histograms of the draws in your output matrices.

\end{enumerate}

\paragraph{Hints}
\begin{itemize}
\item Use \texttt{mvnrnd(theta1,Sigma1)} to draw from a multivariate normal distribution with mean \(\theta_1\) and covariance matrix \(\Sigma_1\).
\item Use \texttt{gamrnd(s1,1/v1,1,1)} to draw from a Gamma distribution with shape parameter \(s_1\) and scale parameter \(v_1\).
\end{itemize}

\paragraph{Readings}
\begin{itemize}
\item \textcite{Chib.Greenberg_1994_BayesInferenceRegression}
\item \textcite[Ch.~10.1]{Greenberg_2008_IntroductionBayesianEconometrics}
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:BayesianEstimationQuarterlyInflation}}
\ifDisplaySolutions%
\input{exercises/bayesian_estimation_quarterly_inflation_solution.tex}
\fi
\newpage
\end{solution}