\section[Information Criteria For AR{(p)}]{Information Criteria For AR{(p)}\label{ex:InformationCriteriaARp}}
Consider the following information criteria to estimate the order \(p\) of an AR{(p)} model: 
\begin{align*}
AIC(n)  &= \log\tilde{\sigma}^2(n) + \frac{2}{T^{eff}}n
\\
SIC(n)  &= \log\tilde{\sigma}^2(n) + \frac{\log T^{eff}}{T^{eff}}n
\\
HQC(n)  &= \log\tilde{\sigma}^2(n) + \frac{2\log \log T^{eff}}{T^{eff}}n
\end{align*}
where \(\tilde{\sigma}^2\) denotes the ML estimate of the variance term
based on the residuals \(\hat{u}_t(n)\) of the corresponding estimated AR{(p)} model.
\(n\) is the number of estimated parameters and \(T^{eff}=T-p^{\text{max}}\),
  where \(p^{\text{max}}\) is the maximum number of lags to consider.

\begin{enumerate}

\item
Provide intuition between the different criteria.
Which one (asymptotically) over- or underestimates the correct order?

\item Write a function \texttt{nlag = lagOrderSelectionARp{(\(y\),\(const\),\(pmax\),\(crit\))}}
  that computes the different order criteria for \(p = 1,\ldots ,p^{\text{max}}\)
  using data vector \(y\) and possible constant term (\(const=1\))
  or constant term and linear trend (\(const=2\)).
\(nlag\) should output the recommended lag according to criteria \(crit\),
  which takes a string (\('AIC'\), \('SIC'\) or \('HQC'\)) as input value.

\item
Load the dataset of the simulated AR{(4)} process given in the CSV file \texttt{AR4.csv}.
Which model is preferred according to the order selection criteria?

\item Simulate another stationary AR{(4)} processes with a different sample size (e.g.\
  \(T = 150\)) and redo the previous exercise.

\end{enumerate}

\paragraph{Readings}
\begin{itemize}
\item \textcite{Lutkepohl_2004_UnivariateTimeSeries}
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:InformationCriteriaARp}}
\ifDisplaySolutions%
\input{exercises/information_criteria_ar_p_solution.tex}
\fi
\newpage
\end{solution}