\section[Maximum Likelihood Estimation of VAR{(p)}]{Maximum Likelihood Estimation of VAR{(p)}\label{ex:MaximumLikelihoodEstimationVARp}}
Consider the VAR{(p)} model with constant written in the more compact form
\begin{align*}
y_t = [c, A_1, \ldots, A_p] Z_{t-1} + u_t = A Z_{t-1}+ u_t
\end{align*}
where \(Z_{t-1}=(1,y_{t-1}',\ldots ,y_{t-p}')'\).
In VAR analysis, it is common to postulate that the innovations, \(u_t\), are iid \(\mathcal{N}(0,\Sigma_u)\) random variables.
This assumption implies that the \(y_t\)'s are also jointly normal
  and, for given initial values \(y_{-p+1},\ldots ,y_{0}\),
\begin{align*}
f_t(y_t|y_{t-1},\ldots ,y_{-p+1})={\left(\frac{1}{2\pi}\right)}^{K/2} {\det(\Sigma_u)}^{-1/2} \exp\left \{ -\frac{1}{2}u_t'\Sigma_u^{-1}u_t \right \}
\end{align*}
Conditional on the first \(p\) observations, the conditional log-likelihood becomes:
\begin{align*}
\log l = -\frac{KT}{2}\log(2\pi) - \frac{T}{2} \log(\det(\Sigma_u))- \frac{1}{2}\sum_{t=1}^T u_t'\Sigma_u^{-1}u_t
\end{align*}
Maximizing this function with respect to the unknown parameters
  yields the Gaussian ML estimators \(\widetilde{A}\) and \(\widetilde{\Sigma_u}\).

\begin{enumerate}
\item Compare the Gaussian ML estimator \(\widetilde{A}\) with the OLS estimator \(\widehat{A}\) from the previous exercise.
Comment on the asymptotic distribution.

\item Provide an expression for the ML estimator \(\widetilde{\Sigma_u}\) of the innovation covariance matrix.

\item Consider data given in \texttt{threeVariableVAR.csv} for \(y_t = (\Delta gnp_t,i_t,\Delta p_t)'\),
  where \(gnp_t\) denotes the log of U.S. real GNP,
  \(p_t\) the corresponding GNP deflator in logs,
  and \(i_t\) the federal funds rate, averaged by quarter.
The estimation period is restricted to 1954q4 to 2007q4. 
\begin{itemize}
\item Estimate the parameters with Maximum Likelihood.
\item Compare your estimation results to an OLS estimation.
\end{itemize}

\end{enumerate}

\paragraph{Readings}
\begin{itemize}
\item \textcite[Ch.~2.3]{Kilian.Lutkepohl_2017_StructuralVectorAutoregressive}
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:MaximumLikelihoodEstimationVARp}}
\ifDisplaySolutions
\input{exercises/ml_var_p_solution.tex}
\fi
\newpage
\end{solution}