\section[RBC model]{RBC model\label{ex:RBCModel}}
Consider the basic Real Business Cycle (RBC) model with leisure.
The representative household maximizes present as well as expected future utility
\begin{align*}
\max E_t \sum_{j=0}^{\infty} \beta^{j} U_{t+j}
\end{align*}
with \(\beta <1\) denoting the discount factor and \(E_t\) is expectation given information at time \(t\).
The contemporaneous utility function 
\begin{align*}
U_t = \gamma \log(c_t) + \psi \log{(1-l_{t})}
\end{align*}
  is additively separable and has two arguments: consumption \(c_t\) and normalized labor supply \(l_{t}\).
The marginal utility of consumption is positive, whereas more labor supply reduces utility.
Accordingly, \(\gamma \) is the consumption weight in the utility function and \(\psi \) the weight on leisure.
In each period the household takes the real wage \(w_t\) as given and supplies perfectly elastic labor service to the representative firm.
In return, she receives real labor income in the amount of \(w_t l_{t}\) and, additionally,
  real profits \({div}_t\) from the firm as well as revenue from lending capital \(k_{t-1}\) at real rental rate \(r_{k,t}\) to the firms,
  as it is assumed that the firm and capital stock are owned by the household.
Income and wealth are used to finance consumption \(c_t\) and investment \(i_t\).
In total, this defines the (real) budget constraint of the household:
\begin{align*}
c_t + i_t = w_t l_{t} + r_{k,t} k_{t-1} + {div}_t
\end{align*}
The law of motion for capital \(k_t\) at the end of period \(t\) is given by
\begin{align*}
k_{t} = (1-\delta) k_{t-1} + i_t
\end{align*}
where \(\delta \) is the capital depreciation rate.\footnote{%
  Note that we use the end-of-period timing convention for capital, i.e.\
    \(k_t\) instead of \(k_{t+1}\),
    because the investment decision is done in period \(t\) and hence capital is also determined in \(t\).
  In older papers and books you will often find beginning-of-period timing convention for capital,
    so always think about when a variable is decided and determined.}
Assume that the transversality condition is full-filled.

Productivity \(a_t\) is the driving force of the economy and evolves according to
\begin{align*}
\log{a_{t}} &= \rho_a \log{a_{t-1}}  + \varepsilon_{a,t}
\end{align*}
where \(\rho_a\) denotes the persistence parameter and \(\varepsilon_{a,t}\) is assumed to be normally distributed with mean zero and variance \(\sigma_a^2\).

Real profits \({div}_t\) of the representative firm are revenues from selling output \(y_t\) minus costs from labor \(w_t l_{d,t}\) and renting capital \(r_{k,t} k_{d,t-1}\):
\begin{align*}
{div}_t = y_{t} - w_{t} l_{d,t} - r_{k,t} k_{d,t-1}
\end{align*}
The representative firm maximizes expected profits
\begin{align*}
	\max E_t \sum_{j=0}^{\infty} {\Lambda}_{t,t+j} {div}_{t+j}
\end{align*}
subject to a Cobb-Douglas production function
\begin{align*}
f(k_{d,t-1}, l_{d,t}) = y_t = a_t k_{d,t-1}^\alpha l_{d,t}^{1-\alpha}
\end{align*}
The stochastic discount factor \({\Lambda}_{t,t+j}\) takes into account that firms are owned by the household,
  i.e.\ it is the present value of a unit of consumption in period \(t+j\) or, respectively,
  the marginal utility of an additional unit of profit;
  therefore
\begin{align*}
\Lambda_{t,t+j}=\beta^j \frac{\partial U_{t+j}/\partial c_{t+j}}{\partial U_{t}/\partial c_{t}}
\end{align*}
Finally, we have non-negativity constraints	\(k_t \geq 0\), \(c_t \geq 0\) and \(0 \leq l_t \leq 1\).

\begin{enumerate}
\item Show that the first-order conditions of the representative household are given by
\begin{align*}
U_{c,t} &= \beta E_t\left[U_{c,t+1} \left(1-\delta + r_{k,t+1}\right)\right]
\\
w_t &= -\frac{U_{l,t}}{U_{c,t}}
\end{align*}
where \(U_{c,t} = \gamma c_t^{-1}\) and \(U_{l,t} = \frac{-\psi}{1-l_t}\).
Interpret these equations in economic terms.

\item Show that the first-order conditions of the representative firm are given by
\begin{align*}
w_t &= f_l
\\
r_{k,t} &= f_k
\end{align*}
where \(f_l = (1-\alpha) a_t {\left(\frac{k_{d,t-1}}{l_{d,t}}\right)}^\alpha \) and \(f_k = \alpha a_t {\left(\frac{k_{d,t-1}}{l_{d,t}}\right)}^{1-\alpha}\).
Interpret these equations in economic terms.

\item Show that combining the optimal decisions with clearing of both the labor market, i.e.\
\(l^s_t = l_t\), and the capital market, \(k^d_t = k_t\) implies clearing of the goods market:
\begin{align*}
y_t = c_t + i_t
\end{align*}  

\item Derive the steady-state of the model, in the sense that there is a set of values for the endogenous variables that in equilibrium remain constant over time.

\item Discuss how to calibrate the following parameters \(\alpha \), \(\beta \), \(\delta \), \(\gamma \), \(\psi \), \(\rho_a\) and \(\sigma_a\).

\item Briefly provide intuition behind the transversality condition.

\item Write a script for this RBC model with a feasible calibration for an OECD country that computes the steady-state of the model.

\item Write a DYNARE mod file for this RBC model with a feasible calibration for an OECD country
  and compute the steady-state of the model by using a \texttt{steady\_state\_model} block.
Compare this to the steady-state computed above.

\item Now assume a contemporaneous utility function of the CRRA (constant Relative Risk Aversion) type:\footnote{%
  Note that due to {L'Hopital}'s rule \(\eta_c=\eta_l=1\) implies the original specification, \(U_t=\gamma \log c_t + \psi \log(1-l_t)\).
}
\begin{align*}
U_t = \gamma \frac{c_{t}^{1-\eta_c}-1}{1-\eta_c} + \psi \frac{{(1-l_{t})}^{1-\eta_l}-1}{1-\eta_l}
\end{align*}
\begin{enumerate}
\item Derive the model equations and steady-state analytically.
\item Write a script to compute the steady-state for this model.
\item Write a DYNARE mod file and compute the steady-state for this model by using a helper function in the \texttt{steady\_state\_model} block.
\end{enumerate}

\end{enumerate}

\paragraph{Readings}
\begin{itemize}
\item \textcite[Ch.~3, Ch.~6]{McCandless_2008_ABCsRBCsIntroduction}
\item \textcite[Ch.~1, Ch.~2]{Torres_2013_IntroductionDynamicMacroeconomic}
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:RBCModel}}
\ifDisplaySolutions%
\input{exercises/rbc_model_solution.tex}
\fi
\newpage
\end{solution}