\section[Non-recursively Identified Models By Short-Run Restrictions]{Non-recursively Identified Models By Short-Run Restrictions\label{ex:NonRecursivelyIdentifiedModelsShortRun}}
Consider a quarterly model of US monetary policy.
Let \(y_t=(\Delta p_t, \Delta gnp_t, i_t, \Delta m_t)'\),
  where \(p_t\) refers to the log of the GNP deflator,
  \(gnp_t\) to the log of real GNP,
  \(i_t\) to the federal funds rate, averaged by quarter,
  and \(m_t\) to the log of money aggregate M1.
The data is given in \texttt{Keating1992.csv}.

The structural shock vector \(\varepsilon_t = (\varepsilon_t^{AS},\varepsilon_t^{IS},\varepsilon_t^{MS},\varepsilon_t^{MD})\)
  includes an aggregate supply shock, an IS shock, a money supply shock, and a money demand shock.
The structural model can be written as:
\begin{align*}
\begin{pmatrix}
u_t^p\\u_t^{gnp}\\u_t^{i}\\u_t^m
\end{pmatrix} = 
\begin{pmatrix}
\varepsilon_{t}^{AS}\\
-b_{21,0}u_t^p - b_{23,0} u_t^i- b_{24,0}u_t^m +\varepsilon_{t}^{IS}\\
-b_{34,0}u_t^m + \varepsilon_{t}^{MS}\\
-b_{41,0}(u_t^{gnp}+u_t^p)-b_{43,0}u_t^i +\varepsilon_{t}^{MD}
\end{pmatrix}
\end{align*}
Furthermore, it is assumed that \(E(\varepsilon_t \varepsilon_t')=\Sigma_{\varepsilon}\) is NOT the identity matrix;
  hence, we will use the normalization rule that the diagonal elements of \(B_{0}\) equal unity.

\begin{enumerate}
\item Estimate the reduced-form covariance matrix of a VAR model with four lags and an intercept with ordinary least squares.

\item Provide intuition behind the structural model and derive the \(B_{0}\) matrix.
Note that we are imposing restrictions on both \(B_{0}\) and \(\Sigma_{\varepsilon} \), but not on \(B_{0}^{-1}\).

\item Estimate \(B_{0}\) and \(\Sigma_{\varepsilon}\) using the nonlinear equation solver \texttt{fsolve}.
To this end, first set up a function that computes
\begin{align*}
F_{SR}([B_{0}, diag(\Sigma_{\varepsilon})]) = \begin{bmatrix} vech\left(B_{0}^{-1} \Sigma_{\varepsilon} B_{0}^{-1'} - \hat{\Sigma}_u\right)\\\text{restrictions on }B_{0}\end{bmatrix}=0
\end{align*}
where \(diag(\Sigma_{\varepsilon})\) denotes only the diagonal elements of \(\Sigma_{\varepsilon}\).
Note that these diagonal elements as well as \(B_{0}\) are stacked into a matrix or vector which is then used as the input for the numerical optimizer.
Use feasible options for the optimizer (e.g.\ as in the previous exercises).

\item Use the estimated structural impact matrix \(B_{0}^{-1}\Sigma_{\varepsilon}^{1/2}\) to plot the structural impulse response functions using \texttt{irfPlots.m}.
Interpret the effects of an aggregate supply shock on prices, real GNP, the Federal Funds rate and M1.
\end{enumerate}

\paragraph{Readings}
\begin{itemize}
\item \textcite[Ch.~8-9]{Kilian.Lutkepohl_2017_StructuralVectorAutoregressive}
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:NonRecursivelyIdentifiedModelsShortRun}}
\ifDisplaySolutions%
\input{exercises/svar_shortrun_solution.tex}
\fi
\newpage
\end{solution}