\section[Visualizing Time Series Data]{Visualizing Time Series Data\label{ex:VisualizingTimeSeriesData}}

\begin{enumerate}
\item What sort of variables are we dealing with in macroeconomics?
\item List sources and providers to get macroeconomic data.
\item Establish a strategy for obtaining macroeconomic data.
\item Analyze the quarterly growth rate of gross domestic product (GDP) for Norway.
To this end, do the following:
\begin{itemize}
	\item Find a source for this data and download it to your computer (preferably as csv or xlsx).
	\item Load the data using MATLAB's interactive import tool. Save the dates and data in two separate variables.
	\item Create a new figure and plot the quarterly growth rate.
	Name it \enquote{Plot of Q-on-Q growth in Norway}.
	\item Create a new figure and plot two histograms, one with 10 bins and another one with 30 bins.
	Call it \enquote{Histogram of Q-on-Q growth in Norway}. Compare them to a fitted normal distribution.
	\item Create a new figure and assess the fit of your data to a normal distribution via a \enquote{Q-Q plot}.
	Call it \enquote{Normal probability plot}.
	\item Create a new figure and plot a boxplot of your data.
	Call it \enquote{Boxplot}.
	\item Give a numerical estimate for the average growth rate and its standard deviation.
\end{itemize}
\item Redo the previous exercise for (i) 1980Q1 to 2012Q4, (ii) 2012Q4 to 2019Q4, and (iii) 2020Q1 to 2022Q2
\item Redo the whole exercise for another country of your choice.
Do a Pull Request on the course's \href{https://github.com/wmutschl/Quantitative-Macroeconomics}{GitHub repository}.
  to upload the used data file (preferably as csv) and your MATLAB script.
\end{enumerate}

\paragraph{Readings}
\begin{itemize}
	\item \url{https://de.mathworks.com/help/matlab/import_export/import-data-interactively.html}
	\item \url{https://de.mathworks.com/help/matlab/import_export/select-spreadsheet-data-interactively.html}
	\item \textcite[Ch.2]{Bjornland.Thorsrud_2015_AppliedTimeSeries}	
\end{itemize}

\paragraph{Useful resources}
\begin{itemize}	
	\item Economic Data Resources (\url{https://libguides.umn.edu/c.php?g=843682&p=6527336})
	\item Gould Library - The Data Search (\url{https://gouldguides.carleton.edu/c.php?g=147179&p=965273})
	\item DBNomics Providers (\url{https://db.nomics.world/providers})
	\item Our World in Data (\url{https://ourworldindata.org})
	\item FRED (\url{https://fred.stlouisfed.org})
\end{itemize}

\begin{solution}\textbf{Solution to \nameref{ex:VisualizingTimeSeriesData}}
\ifDisplaySolutions
\input{exercises/visualizing_time_series_data_solution.tex}
\fi
\newpage
\end{solution}